Separating Use and Reuse to Improve Both

### 2017-05-19 FACS/Intro.tex
.

\begin{figure}[t]
\begin{center}
\begin{tabular}{c|c|c|c}
              & Instantiable (Use) & Unit of Reuse & Introduces New Type \\
\hline
Class  & Yes              & No          & Yes           \\
Trait   & No               & Yes         & No            \\
\end{tabular}
\end{center}
\caption{A comparision between traits and classes in \name.}
\label{fig:compare}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\begin{tabular}{c|c|c|c}
              & Instantiable (Use) & Unit of Reuse & Introduces New Type \\
\hline
Class  & Yes              & No          & Yes           \\
Trait   & No               & Yes         & No            \\
\end{tabular}
\end{center}
More complete table here, we can put it where you prefer
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c|c|c}
&\Rotated{direct instantation}
&\Rotated{self instantiation}
&\Rotated{unit of use}
&\Rotated{unit of reuse}
&\Rotated{introduce type}
&\Rotated{induced type is this type}
&\Rotated{binary methods}
&\Rotated{reuse induce subtype}
&\Rotated{well-typed before imported}
&\Rotated{well-typed before composed} 
\\
\hline
java/scala class&Y&X&Y&Y&Y&Y&X&Y&Y&X\\
java8 interface &X&X&X&Y&Y&Y&X&Y&Y&X\\
scala trait        &X&X&X&Y&Y&Y&X&Y&X&X\\
original trait     &X&X&X&Y&-&-&X&X&-&-\\
Ferruccio trait  &X&X&X&Y&X&-&X&X&Y&Y\\
42 trait            &X&Y&X&Y&X&-&Y&X&Y&X\\
42 class           &Y&Y&Y&X&Y&Y&Y&-&Y&X\\
module composition
                      &-&-&Y&Y&-&-&-&-&Y&Y\\
deepFJig class &Y&Y&Y&Y&Y&X&Y&X&Y&Y\\
package template
                      &X&Y&X&Y&X&-&X&X&Y&X\\

\end{tabular}
\end{center}

\caption{A comparision between traits and classes in \name.}
\label{fig:compare}
\end{figure}
